Deterministic contention management for low latency Cloud RAN over an optical ring

### 2019-01-17 v3/articleV3.tex
debut texte

There are two sources of inefficiency in this method. The first comes from the reservation and cannot be avoided to guarantee the latency of the C-RAN traffic. The second comes from the fact that an RRH must emit at the same position during all the emission time (to guarantee zero latency). If we allow to change the position of data coming from the same RRH during the period, 
we can use \emph{all} containers in a given position and hence we could support $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$ antennas.

@@

>>>>

There are two sources of inefficiency in this method. The first comes from the reservation and cannot be avoided to guarantee the latency of the C-RAN traffic. The second comes from the fact that an RRH must emit at the same position during all the emission time (to guarantee zero latency). In Sec.~\ref{sec:maxant}, we propose an approach to allow to change the position of data coming from the same RRH during the period, that helps to maximize the number of antennas supported by the ring.

@@

\section{A smarter approach for N-GREEN parameters}
\label{sec:maxant}

The previous approach limits the number of antennas supported by the ring when $ET \geq \frac{P-RS}{2}$ which is the case with N-GREEN parameters. In order to maximize the number of antennas, we now want to allow the datas from a same RRH to use different positions in the slot.

In order to allow as much antennas as possible on the ring, the idea is to use \emph{all} containers in a given position. To do so we do the compacting positions of previous section and when less than $ET$ free containers remain in a position ( let us call $x$ this number of free containers), then the $x$ first containers of an antenna are assigned to this position, and the $ET - x$ last containers of this antennas are assigned to the next position. Fig.~\ref{fig:split} illustrates this manner to find an assignment with a maximal number of antennas. The number of antennas supported by the ring is now  $\lfloor\frac{P- RS}{ET} \times \frac{F}{2}\rfloor$.

      \includegraphics[scale=0.8]{split}
     \caption{Assignment with $9$ antennas with the N-GREEN parameters.}   \label{fig:split}
\end{center}
  \end{figure}
